Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases

### 2025-05-12 endofquarterpaper.qmd
stash

---
title: "Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases"
author: Sophie Cooper
format: docx
echo: false
execute: 
  warning: false
bibliography: references.bib
link-citations: true
---

>>>>

---
title: "Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases"
author: Sophie Cooper
format: html
echo: false
execute: 
  warning: false
bibliography: references.bib
link-citations: true
---
